Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-01-30 hscc2017/paper.tex
address comment regarding the fact that the CEGIS solution space is finite but potentially very large

%\renewcommand{\baselinestretch}{0.975}
\allowdisplaybreaks
\include{macros}

@@

% Copyright
\setcopyright{acmcopyright}

% DOI
\doi{}

% ISBN
\isbn{}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{
Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
Plants%
\thanks{Supported by EPSRC grant EP/J012564/1
and ERC project 280053 (CPROVER).}
%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

It is
worth noting that each iteration of the loop adds a new input to the
finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
the full set of inputs $\mathcal{D}$
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

>>>>

\renewcommand{\baselinestretch}{0.99}
\allowdisplaybreaks
\include{macros}

@@

\CopyrightYear{2017}
\setcopyright{acmcopyright}
\conferenceinfo{HSCC '17,}{April 18--20, 2017, Pittsburgh, PA, USA.}
\isbn{978-1-4503-4590-3/17/04}\acmPrice{\$15.00.}
\doi{TDB.}

\title{
Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
Plants%
\thanks{Supported by EPSRC grant EP/J012564/1
and ERC project 280053 (CPROVER).}}

%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

It is worth noting that each iteration of the loop adds a new input to
the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
that the full set of inputs $\mathcal{D}$ is finite, this means that
the refinement loop can only iterate a potentially very large, but
finite number of times.
